The globular cluster system of the Auriga simulations

### 2019-06-13 AurigaGCS.tex
First version of the introduction done

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Auriga GCS]{The Globular Cluster System of the Auriga Simulations}

@@

We now turn to recent studies that focus on the hypothesis that the physical 
processes responsible for the formation of young massive clusters (YMC)s (observable)
in the local Universe also governs GC formation at high redshifts and differences
between both classes of objects are caused by nearly a Hubble time of (dynamical)
evolution. This picture is based on observed similarities between YMCs and GCs
\citep[e.g.][]{1992AJ....103..691H}, % Schweizer+ 1996, Whitmore+ 1999, Bastian+ 2006
and strengthened by observations of gravitationally lensed objects at high redshifts
($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
GC progenitors at times of formation (Vanzella et al. 2017; Johnson et al. 2017).
Early modelling work by \citet{2015MNRAS.454.1658K} is now incorporated into
cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

Recent studies by other groups also incorporate formation of (globular) star 
clusters into cosmological zoom simulations.
\todo[inline]{
Cosmological Galform simulations (e.g. Oser et al. 2010; Cook et al. 2016; 
Rodriguez-Gomez et al. 2016), in situ vs. ex situ, particle tagging.}

\citep{2005ApJ...623..650K}
\citep{2016ApJ...831..204R}
\citep{2017ApJ...834...69L}
\citep{2017MNRAS.465.3622R}
\citep{2018MNRAS.474.4232K}
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}

\citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}

@@

\todo[inline]{Paragraph: Paper outline}
We summarise the relevant characteristics of the Auriga simulations in
section~\ref{sec:auriga}, followed by a summary of the observations of the
Milky Way (MW) and Andromeda globular cluster system (GCS) in
section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

@@

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.

\todo[inline]{Check Auriga boilerplate that we need to acknowledge}
RG and VS acknowledge support by the DFG Research Centre SFB-881 `The
Milky Way System' through project A1. This work has also been
supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the
SuperMUC system at the Leibniz Computing Centre, Garching,
under the project PR85JE of the Gauss Centre for Supercomputing.
This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology
on behalf of the STFC DiRAC HPC Facility `www.dirac.ac.uk'.
This equipment was funded by BIS National E-infrastructure capital
grant ST/K00042X/1, STFC capital grant ST/H008519/1 and
STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.

@@

\bibliographystyle{mnras}
\bibliography{AurigaGCS} % if your bibtex file is called example.bib

@@

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
\clearpage
\appendix
\section{Scatter between individual Auriga haloes, and numerical convergence}
\label{sec:scatter-convergence}
We check whether the properties of the Auriga globular cluster candidates
are well converged between the three different resolution levels used for the
Auriga simulations. Here we consider all three Auriga haloes for which simulation
runs were performed at all three resolution levels: Au6, Au16, and Au24. Here
we can investigate differences between individual haloes.

Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution,
Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
Figure~\ref{fig:logMRgcFeH_res}

\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
    \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
        halo, where colours indicate the resolution level: L3 green, L4 orange,
        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
        \emph{Right:} Auriga halo 24. For all three haloes we find marginal
        increases in the mass normalization with increasing resolution level.
        \label{fig:logMFeH_res}
    }

\end{figure*}
\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
    \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga
        halo, where colours indicate the resolution level: L3 green, L4 orange,
        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
        \emph{Right:} Auriga halo 24. For all three haloes we find marginal
        increases in the mass normalization with increasing resolution level.
        \label{fig:logMRgc_res}
    }

\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Auriga GCS]{The globular cluster system of the Auriga simulations}

@@

An idea that has recently been studied in detail is the hypothesis that the physical 
processes responsible for the formation of young massive clusters \citep[YMCs, 
see][for a review]{2010ARA&A..48..431P}, observable in the local Universe in great
detail, also governs GC formation at high redshifts. In this framework, differences
between both classes of objects are caused by nearly a Hubble time of (dynamical)
evolution \citep[e.g.][]{1987degc.book.....S}. This picture is based on observed 
similarities between YMCs and GCs \citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W}
and strengthened by observations of gravitationally lensed objects at high redshifts
($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
GC progenitors at times of formation \citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}.
The modelling work by \citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} 
is now incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

Simulation resolutions have reached the mass range populated by GCs, and the
gravitational force softening can be as low several parsec. A number of groups 
can thus incorporate formation of (globular) star clusters into their 
high-resolution hydrodynamical cosmological zoom simulations. \citet{
2016ApJ...831..204R} run parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
\citet{2019MNRAS.482.4528E}.

@@

In this work we use state of the art simulations that produce realistic 
spiral galaxies at redshift zero that reproduce a number of observables. Therefore
the question naturally arises whether the simulations (also) yield a population 
of star particles that is consistent with the Milky Way and/or Andromeda globular 
cluster systems. In particular, we investigate the Auriga suite of cosmological 
zoom simulations (\citealt{2017MNRAS.467..179G}, and described in 
Sec.~\ref{sec:auriga}) which can serve as an ultimate test of the star formation 
model implemented in these simulations. The plan of the paper is as follows. We
summarise the relevant characteristics of the Auriga simulations in
section~\ref{sec:auriga}, followed by a summary of the observations of the
Milky Way (MW) and Andromeda globular cluster system (GCS) in
section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

@@

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.
\todo[inline]{Check Auriga boilerplate that we need to acknowledge}
RG and VS acknowledge support by the DFG Research Centre SFB-881 `The
Milky Way System' through project A1. This work has also been
supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the
SuperMUC system at the Leibniz Computing Centre, Garching,
under the project PR85JE of the Gauss Centre for Supercomputing.
This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology
on behalf of the STFC DiRAC HPC Facility `www.dirac.ac.uk'.
This equipment was funded by BIS National E-infrastructure capital
grant ST/K00042X/1, STFC capital grant ST/H008519/1 and
STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.

The analysis in this work was performed using the Python \citep{python}
programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
the Numpy \citep{2011CSE....13b..22V}, Scipy \citep{scipy}, and Astropy 
\citep{2013A&A...558A..33A} packages. Plots were generated using 
Matplotlib \citep{2007CSE.....9...90H}.

@@

\bibliographystyle{mnras}
\bibliography{AurigaGCS}

@@

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
% \clearpage
% \appendix
% \section{Scatter between individual Auriga haloes, and numerical convergence}
% \label{sec:scatter-convergence}
% We check whether the properties of the Auriga globular cluster candidates
% are well converged between the three different resolution levels used for the
% Auriga simulations. Here we consider all three Auriga haloes for which simulation
% runs were performed at all three resolution levels: Au6, Au16, and Au24. Here
% we can investigate differences between individual haloes.
% 
% Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution,
% Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
% Figure~\ref{fig:logMRgcFeH_res}
% 
% 
% 
% \begin{figure*}
%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
%     \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
%         halo, where colours indicate the resolution level: L3 green, L4 orange,
%         and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
%         \emph{Right:} Auriga halo 24. For all three haloes we find marginal
%         increases in the mass normalization with increasing resolution level.
%         \label{fig:logMFeH_res}
%     }
% 
% \end{figure*}
% \begin{figure*}
%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
%     \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga
%         halo, where colours indicate the resolution level: L3 green, L4 orange,
%         and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
%         \emph{Right:} Auriga halo 24. For all three haloes we find marginal
%         increases in the mass normalization with increasing resolution level.
%         \label{fig:logMRgc_res}
%     }
% 
% \end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
